Clustering analysis and statistics

### 2019-06-12 notebooks/Clustering analysis.Rmd
minor changes

```{r import data}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-415-2-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S",
  "2014-01-1741-1-S"
  )

@@

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F)
  filter(id %not_in% ex_samples)

# cgMLST data
cgmlst_stats <- read.table("../data/chewbbaca/complete_results/mdata_stats.tsv",
                         sep = "\t",
                         header = TRUE,
                         stringsAsFactors = FALSE) %>%
  filter(FILE != "2016-02-415_S208_pilon_spades.fasta")

detailed_cgmlst_stats <- read.table("../data/chewbbaca/results_statistics.tsv",
                                    sep = "\t",
                                    header = TRUE,
                                    stringsAsFactors = FALSE) %>%
  filter(Genome != "2016-02-415_S208_pilon_spades.fasta")

@@

```{r}
test <- detailed_cgmlst_stats %>%
  gather(metric, value, -Genome) %>%
  group_by(metric) %>%
  mutate(mean_val = round(mean(value), 1))

>>>>

```{r import data}
# Vector of excluded samples
ex_samples <- c(
  "2016-17-565-1-S",
  "2016-02-428-2-S",
  "2016-02-486-2-S",
  "2016-02-732-2-S",
  "2014-01-1741-1-S"
  )

@@

isolate_data <- read.table("../data/isolate_data.txt",
                           sep = "\t",
                           header = T,
                           stringsAsFactors = F) %>%
  filter(id %not_in% ex_samples)

# cgMLST data
cgmlst_stats <- read.table("../data/chewbbaca/complete_results/mdata_stats.tsv",
                         sep = "\t",
                         header = TRUE,
                         stringsAsFactors = FALSE)

detailed_cgmlst_stats <- read.table("../data/chewbbaca/results_statistics.tsv",
                                    sep = "\t",
                                    header = TRUE,
                                    stringsAsFactors = FALSE) %>%
  mutate(sums = rowSums(.[,4:8]))

@@

```{r, message=FALSE, warning=FALSE}
test <- detailed_cgmlst_stats %>%
  gather(metric, value, -Genome) %>%
  group_by(metric) %>%
  mutate(mean_val = round(mean(value), 1))
